---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


<!-- badges: start -->
[![Build Status](https://travis-ci.org/vincenzocoia/powers.svg?branch=master)](https://travis-ci.org/vincenzocoia/powers)
[![Codecov test coverage](https://codecov.io/gh/vincenzocoia/powers/branch/master/graph/badge.svg)](https://codecov.io/gh/vincenzocoia/powers?branch=master)
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
<!-- badges: end -->

__Note__: The real purpose of this R package is for demonstrating how to make an R package.

# powers

This is an R package that gives `sqrt()` some friends by providing other power functions. The purrr package is used under the hood, so that either an (atomic) vector or a list can be input. 

## Installation

You can install powers from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("vincenzocoia/powers")
```

## Example

See the vignette for more extensive use, but here's an example:

```{r example}
reciprocal(2)
cube(list(1, 4, 5))
```
